The data is hosted on UCI Machine Learning Repository and is named as – Census Income Data Set, sometimes referred as ‘Adult Dataset’. After getting data, we are doing some cleanup, plotting data and applying different algorithms

```{r}
csvData <- read.csv("income.csv")
head(csvData)
colnames(csvData) <- c("age", "workclass", "fnlwgt", "education", "education-num", "marital-status", "occupation", "relationship", "race", "sex", "capital-gain", "capital-loss", "hours-per-week", "native-country", "income")
head(csvData)

```
Delete rows with missing values

```{r}
#unique(csvData$workclass)
#unique(csvData$occupation)
#unique(csvData$`native-country`)
csData <- csvData[!grepl(" \\?", csvData$workclass),]
csvData <- csvData[!grepl(" \\?", csvData$occupation),]
csvData <- csvData[!grepl(" \\?", csvData$`native-country`),]
str(csData)
```
Reduce number of sample to 2000

```{r}
csvData <- csvData[1:2000,]
```


Map output values to numeric

```{r}
strings <- sort(unique(csvData$income))
numbers <- 0:(length(strings) - 1)
names(numbers) <- strings
csvData$incomenum <- numbers[csvData$income]
```

Output data distribution

```{r}
#install.packages("ggplot2")
library(ggplot2)
#install.packages("gridExtra")
library(gridExtra)
ggplot(csvData, aes(x=csvData$incomenum)) + geom_histogram(color = "black", fill = "red", bins=10)
```

Input data distribution

```{r}
plot1 <- ggplot(csvData, aes(x=csvData$age, fill=factor(csvData$income))) + geom_bar()  + labs(x="Age", y="Count")
plot2 <- ggplot(csvData, aes(x=csvData$workclass, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + labs(x="Workclass", y="Count")
plot3 <- ggplot(csvData, aes(x=csvData$fnlwgt, y=factor(csvData$income))) + geom_point() + labs(x="fnlwgt", y="Income level")
plot4 <- ggplot(csvData, aes(x=csvData$education, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Education", y="Count")
plot5 <- ggplot(csvData, aes(x=csvData$`education-num`, fill=factor(csvData$income))) + geom_bar() + labs(x="Years of Education", y="Count")
plot6 <- ggplot(csvData, aes(x=csvData$`marital-status`, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Marital Status", y="Count")
plot7 <- ggplot(csvData, aes(x=csvData$occupation, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Occupation", y="Count")
plot8 <- ggplot(csvData, aes(x=csvData$relationship, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Relationship", y="Count")
plot9 <- ggplot(csvData, aes(x=csvData$relationship, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
plot10 <- ggplot(csvData, aes(x=csvData$race, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

plot11 <- ggplot(csvData, aes(x=csvData$sex, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Sex", y="Count")
plot12 <- ggplot(csvData, aes(x=csvData$`capital-gain`, y=factor(csvData$income))) + geom_point() + labs(x="capital-gain", y="Income level")
#plot13 <- ggplot(csvData, aes(x=csvData$`capital-loss`, y=factor(csvData$income))) + + geom_point() + labs(x="capital-loss", y="Income level")
plot14 <- ggplot(csvData, aes(x=csvData$`hours-per-week`, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Hours Per Week", y="Count")
plot15 <- ggplot(csvData, aes(x=csvData$`native-country`, fill=factor(csvData$income))) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ labs(x="Native Country", y="Count")
 
#grid.arrange(plot7, plot8, ncol=1)
#grid.arrange(plot9, plot10, ncol=1)
#grid.arrange(plot11, plot12, ncol=1)
#grid.arrange(plot13, plot14, ncol=1)
#grid.arrange(plot15, ncol=1)
plot10
plot15
```

Create	train	and	test	data	sets

```{r}
numrow <- nrow(csvData)
rand <- sample(1:numrow)
cutPoint <- floor(2*numrow/3)
trainData <- csvData[rand[1:cutPoint],]
testData <- csvData[rand[(cutPoint+1):numrow],]
```
Linear Model 
```{r}
trainData$incomenum <- as.factor(trainData$incomenum)
lmOut <- glm(formula = incomenum ~ age+workclass+education+occupation+relationship+sex+`hours-per-week`, data=trainData, family=binomial(link='logit') )
summary(lmOut)
fitted.results <- predict(lmOut,testData, type="response")
lmPredict <- ifelse(fitted.results > 0.5,1,0)

misClasificError <- mean(lmPredict != trainData$incomenum)
print(paste('Accuracy',1-misClasificError))
```


Modelling techniques for classification

```{r}
#install.packages("kernlab")		
library(kernlab)

ksvmOut <- ksvm(income ~ age+workclass+education+`education-num`+`marital-status`+occupation+relationship+race+sex+`hours-per-week`, data=trainData, kernel="rbfdot", kpar="automatic", C=5, cross=3, prob.model=TRUE)
ksvmPred <- predict(ksvmOut, testData)
compTable <- table(data.frame(testData$income, ksvmPred))
compTable
predictionAccuracy <- (compTable[1,1]+compTable[2,2])/667 * 100
predictionAccuracy
prediction1 <- as.factor(ifelse(ksvmPred == testData$income, "No Error", "Error"))
plot1 <- plot(prediction1, width=3, main="SVM", ylab="No of samples")
plot1

library(gridExtra)
#install.packages("e1071")
library(e1071)

nbOut <- naiveBayes(formula=income ~ age+workclass+education+`education-num`+`marital-status`+occupation+relationship+race+sex+`hours-per-week`, data=trainData)
nbPred <- predict(nbOut, testData)
testData[testData$income == nbPred,]
testData[testData$income != nbPred,]
compTable <- table(data.frame(testData$income, nbPred))
predictionAccuracy <- (compTable[1,1]+compTable[2,2])/667 * 100
prediction3<- as.factor(ifelse(nbPred == testData$income, "No Error", "Error"))
plot2 <- plot(prediction3, width=3, main="Naive Bayes", ylab="No of samples")
plot2
```

Associative rules

```{r}
#install.packages("arules")
library(arules)

#install.packages("arulesViz")
#library(arulesViz)
str(csvData)
discreteData <- data.frame(csvData$workclass, csvData$education, csvData$`marital-status`, csvData$occupation, csvData$relationship, csvData$race,
                           csvData$sex, csvData$`native-country`, csvData$income)
rules <- apriori(discreteData, parameter = list(support=0.50, confidence=0.80))
inspect(rules)
```